---
title: "Week 2 Notes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Coding Standards in R
Write code using text editor and text file
Indent your code (8 spaces)
Limit the width of your code (80 columns)
Limit the length of functions - one basic activity 

##Markdown
*italics*  
**bold**  
#Main heading  
## secondary heading  
### this is a tertiary heading  

- first item in a list
- second item in list
- third iten in list

1. first
2. second
3. third

[text](url)

Advanced linking
[text][1] and [text][2]
[1]: url "text"
[2]: url "text"

Newlines
Firt line  (double space after the end of a line)  
Second line

##R markdown
play on the word markup language
designed to help you write things
created by John Gruber

R Markdown
allows on to create documents containing "live" R code
R code is evaluated as part of the processing of the markdown
Results from R code are inserted into markdown document
A core tool in literate stastical programming 

R markdown can be converted to standard markdown using the knitr package
Create slides in R Markdwon using slidify

R markdown >> markdown >> html

Never edit intermediate file or html file

## Literate Stastical Programming 
Put the data and the code together in the same document
Have a single document that integrates the data analysis 

Original idea came from Don Knuth  
an article is a stream of text and code  
weave <- human readable  
tangle <- machine readable  

Original Sweave used LaTeX and R  

Keep track of things, perhaps with a version control system to track   snapshots/changes  
Use software whose operation can be coded  
Don't save output  
Save data in non-proprietary formats   

##knitr
R package written by Yihui Xie  
Supports rMarkdown, LaTeX, and HTML  
can export to PDF, HTMK  
Built right into RStudio for your convenience  

knit 2 html("document.Rmd")  

####A few notes
knitr will fill a new doc with filler text. DELETE IT
All R code goes between markers
Code chunks can have numes
{r firstchunk, echo = FALSE, results = "hide"}

#My first knitr doc
##Introduction
Sys.time()  

{r scatterplot, fig.height =4}  

knitr produces an HTML file  

```{r table, results = "asis"}
library(xtable)
xt <- xtable(summary(fit))
print(xt, type = "html")
```
Can set Global Option

{r setoptions, echo=FALSE}
opts_chunk$set(exho = FALSE, results = "hide")

cache the computation
cache=TRUE
after first run, results are loaded from cache
dependencies are not checkd explicitly 


